Exploratory Plots

### 2020-09-04 exploratory/2020/sub3_fit_subsets.Rmd
Update plots with results from 1 seed & fixed bug in fraction mapped code

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```

>>>>

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=ref_weight, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("dataset", nrow = 1) + 
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```
